---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# NINA

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/agarciaEE/NINA.svg?branch=main)](https://travis-ci.com/agarciaEE/NINA)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/agarciaEE/NINA?branch=main&svg=true)](https://ci.appveyor.com/project/agarciaEE/NINA)
[![Codecov test coverage](https://codecov.io/gh/agarciaEE/NINA/branch/main/graph/badge.svg)](https://codecov.io/gh/agarciaEE/NINA?branch=main)
<!-- badges: end -->

The goal of NINA is the the analysis and implementation of biotic interactions into environmental niche models using kernel density estimations. 

## Installation

You can install the released version of NINA from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("NINA")
```

## Example

This is a basic example which shows you how to use NINA's functions:

```{r load}
library(NINA)
## basic example code
```

Estimate Environmental Niche Models:

```{r ENmodels}
g1_EN = EN_model(env_data, occ_data1)
g2_EN = EN_model(env_data, occ_data2)
```

Correct EN models by biotic interactions:

```{r BCmodels}
g2_BC <- BC_model(g2_EN, g1_EN, A.matrix = int_matrix,  type = "global")

```

Transform environmental niche space into ecological niche space (prioritizing the effect of biotic interactions).

```{r ECmodels}
g2_EC <- EC_model(g2_BC, type = "global")
```

You can summarize the output by using `summary` function or `print`:
```{r summary}
summary(g1_EN)
print(g2_BC)
```

You can also plot a summary of the output model using `plot` function:

```{r plot, echo = FALSE}
plot(g2_BC)
```

Models can be evaluated using NINA's function `models_evaluation` and visualize it by plotting the output.

```{r eval}
eval <- models_evaluation(g2_BC, plot = F)
plot(eval)
````

