---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# NINA package

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/agarciaEE/NINA.svg?branch=main)](https://travis-ci.com/agarciaEE/NINA)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/agarciaEE/NINA?branch=main&svg=true)](https://ci.appveyor.com/project/agarciaEE/NINA)
[![Codecov test coverage](https://codecov.io/gh/agarciaEE/NINA/branch/main/graph/badge.svg)](https://codecov.io/gh/agarciaEE/NINA?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/NINA)](https://CRAN.R-project.org/package=NINA)
<!-- badges: end -->

The goal of NINA is the the analysis and implementation of biotic interactions into environmental niche models using kernel density estimations. 

## Installation

You can install NINA from github repository with:

``` r
devtools::install_github("agarciaEE/NINA")

```

## Example

This is a basic example which shows you how to use NINA's functions:

Estimate Environmental Niche Models:

```{r ENmodels, include = F}
library(NINA)
g1_EN = EN_model(env_data, occ_data1, cluster = "env", n.clus = 5)
g2_EN = EN_model(env_data, occ_data2, cluster = g1_EN$clus)
```

Correct EN models by biotic interactions:

```{r BCmodels}
g2_BC <- BC_model(g2_EN, g1_EN, A.matrix = int_matrix, type = "region")

```

Transform environmental niche space into ecological niche space (prioritizing the effect of biotic interactions).

```{r ECmodels}
g2_EC <- EC_model(g2_BC, type = "region")
```

You can summarize the output by using `summary` function or `print`:
```{r summary}
summary(g1_EN)
print(g2_BC)
```

You can also plot a summary of the output model using `plot` function:

```{r plot}
plot(g2_EN)
```

Models can be evaluated using NINA's function `models_evaluation` and visualize it by plotting the output.

